Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-26 paper/output/regressions/robustness_50y.tex
#29 change window header

\begin{table}[htbp]
   \caption{\label{tab:robustness_50y} Heterogeneous effects of switching: More robustness}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variable: & \multicolumn{4}{c}{All construction}\\
                                                 & Baseline & 4 switches   & All switches & Window \\   
      Model:                                     & (1)      & (2)          & (3)          & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02     & 0.04$^{***}$ & 0.02$^{***}$ & 0.02\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.02)\\   
      Switch to another state $\times$ Conquest  & 0.04     & 0.03         & -0.01        & 0.04\\   
                                                 & (0.04)   & (0.02)       & (0.01)       & (0.04)\\   
      Switch to another state $\times$ Other     & 0.01     & -0.02        & 0.00         & 0.01\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.03)\\   
      Switching indicator                        & -0.01    & -0.02        & -0.01        & -0.01\\   
                                                 & (0.02)   & (0.02)       & (0.01)       & (0.02)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes      & Yes          & Yes          & Yes\\  
      Period                                     & Yes      & Yes          & Yes          & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 6,635    & 12,979       & 31,754       & 6,635\\  
      R$^2$                                      & 0.3553   & 0.3664       & 0.3518       & 0.3553\\  
      Within R$^2$                               & 0.0009   & 0.0019       & 0.0003       & 0.0009\\  
      \midrule \midrule

>>>>

\begin{table}[htbp]
   \caption{\label{tab:robustness_50y} Heterogeneous effects of switching: More robustness}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variable: & \multicolumn{4}{c}{All construction}\\
                                                 & Baseline & 4 switches   & All switches & 200 years \\   
      Model:                                     & (1)      & (2)          & (3)          & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02     & 0.04$^{***}$ & 0.02$^{***}$ & 0.02\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.02)\\   
      Switch to another state $\times$ Conquest  & 0.04     & 0.03         & -0.01        & 0.04\\   
                                                 & (0.04)   & (0.02)       & (0.01)       & (0.04)\\   
      Switch to another state $\times$ Other     & 0.01     & -0.02        & 0.00         & 0.01\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.03)\\   
      Switching indicator                        & -0.01    & -0.02        & -0.01        & -0.01\\   
                                                 & (0.02)   & (0.02)       & (0.01)       & (0.02)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes      & Yes          & Yes          & Yes\\  
      Period                                     & Yes      & Yes          & Yes          & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 6,635    & 12,979       & 31,754       & 6,635\\  
      R$^2$                                      & 0.3553   & 0.3664       & 0.3518       & 0.3553\\  
      Within R$^2$                               & 0.0009   & 0.0019       & 0.0003       & 0.0009\\  
      \midrule \midrule
